Convolutional equivalent layer for gravity data processing

### 2020-08-07 manuscript/synthetic_data.tex
include EIC and reviewer #3 comments/corrections

We performed the upward and downward continuations of the simulated gravity data 
(Figure \ref{fig:synthetic_data}) by using the fast equivalent-layer technique
\citep{siqueira-etal2017}, our method and also the classical approach in the 
Fourier domain. This approach consists in performing the upward/downward continuation 
by directly computing the Fourier transform of the gravity data 
\citep[e.g., ][ p. 317]{blakely1996}.
Figure \ref{fig:upward_comparison} shows the upward-continued gravity data 
obtained by the three methods.
As we can see, the residuals between the true data at $z = -300$ m 
(Figure \ref{fig:upward_comparison}a) and the upward-continued data obtained by 
using our method (Figure \ref{fig:upward_comparison}b) and 
the fast equivalent-layer technique (Figure \ref{fig:upward_comparison}c) are very similar 
to each other.
Notice that the absolute values of the residuals produced by the classical Fourier 
approach (Figure \ref{fig:upward_comparison}d) are $\approx 10$ times greater than
those produced by our method and the fast equivalent-layer technique 
(Figure \ref{fig:upward_comparison}b and \ref{fig:upward_comparison}c), 
with maximum values concentrated at the border of the simulated area.
Differently from the results yield by our method (Figure \ref{fig:upward_comparison}b) 
and the fast equivalent-layer technique (Figure \ref{fig:upward_comparison}c), 
that obtained with the classical Fourier approach exhibits a slight noise 
amplification (Figure \ref{fig:upward_comparison}d).

@@

We opted for showing all the results (Figures \ref{fig:upward_comparison} and 
\ref{fig:downward_comparison}) produced by all methods without removing the border 
effects in order to properly compare them to each other.
We also stress that no padding function to expand the data was used in applying 
our method, the fast equivalent-layer technique or the Fourier approach.
Another important aspect to be pointed out about these results 
is the computational times spent by our method and the fast equivalent-layer technique. 
The total computational time required by our method to estimate the physical-property 
distribution on the equivalent layer and to perform the upward/downward continuations 
is about two orders of magnitude lower than that spent by the fast equivalent-layer technique.
This significant reduction in computational time was obtained by using a data set 
composed of $N = 10,000$ observation points. Considerably better results can be 
obtained with larger data sets.

Finally, we did not compare the total computational times spent by our method 
and the classical Fourier approach, but we can affirm that the second is smaller. 
Because  the Fourier approach requires only one DFT/IDFT of the data, whereas 
our method requires one DFT/IDFT per iteration, it is computationally faster 
than our method.
However, the considerably smaller noise amplification and practically nonexistent 
border effect are the main advantages of our method over the classical Fourier 
approach, especially in the downward continuation.

>>>>

We performed the upward and downward continuations of the simulated gravity data 
(Figure \ref{fig:synthetic_data}) by using the fast equivalent-layer technique
\citep{siqueira-etal2017}, our method and also the classical approach in the 
Fourier domain. This approach consists in performing the upward/downward continuation 
by directly computing the Fourier transform of the gravity data 
\citep[e.g., ][ p. 317]{blakely1996}.
Figure \ref{fig:upward_comparison} shows the upward-continued gravity data 
obtained by the three methods.
As we can see, the residuals between the true data at $z = -300$ m 
(Figure \ref{fig:upward_comparison}a) and the upward-continued data obtained by 
using our method (Figure \ref{fig:upward_comparison}b) and 
the fast equivalent-layer technique (Figure \ref{fig:upward_comparison}c) are very similar 
to each other.
Note that the absolute values of the residuals produced by the classical Fourier 
approach (Figure \ref{fig:upward_comparison}d) are $\approx 10$ times greater than
those produced by our method and the fast equivalent-layer technique 
(Figure \ref{fig:upward_comparison}b and \ref{fig:upward_comparison}c), 
with maximum values concentrated at the border of the simulated area.
Differently from the results yield by our method (Figure \ref{fig:upward_comparison}b) 
and the fast equivalent-layer technique (Figure \ref{fig:upward_comparison}c), 
that obtained with the classical Fourier approach exhibits a slight noise 
amplification (Figure \ref{fig:upward_comparison}d).

@@

We opted for showing all the results (Figures \ref{fig:upward_comparison} and 
\ref{fig:downward_comparison}) produced by all methods without removing the border 
effects in order to properly compare them to each other.
We also stress that no padding function to expand the data was used in applying 
our method, the fast equivalent-layer technique or the Fourier approach.
It is important to stress that the Fourier method shows heavy border effects at large 
altitudes if no padding is made \citep{baniamerian_etal2017}. 
Another important aspect to be pointed out about these results 
is that the computational time required by our method to estimate the physical-property 
distribution on the equivalent layer and to perform the upward/downward continuations 
is about two orders of magnitude lower than that spent by the fast equivalent-layer technique.
This significant reduction in computational time was obtained by using a data set 
composed of $N = 10,000$ observation points. Considerably better results can be 
obtained with larger data sets.

Finally, we did not compare the total computational times spent by our method 
and the classical Fourier approach, but we can affirm that the second is smaller. 
Because  the Fourier approach requires only one DFT/IDFT of the data, whereas 
our method requires one DFT/IDFT per iteration, the former is computationally faster 
than our method.
However, the considerably smaller noise amplification and practically nonexistent 
border effects obtained without applying any padding function to expand 
the data are the main advantages of our method over the classical Fourier 
approach, especially in the downward continuation.
